---
title: "Supplementary Test Code"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains the code for the advert-level variations, which is included as a supplementary test to the main analysis. 


## Persuasion knowledge: interaction version*training model 

Showing the different levels of increase in persuasion knowledge across the different adverts, testing if there is an interaction effect?

```{r include=FALSE}

#plotting the random effects interaction for ainform_pk3

imprint_df$predicted_PK <- predict(ainform_pk3, re.form = NULL)

mean_predicted_values <- imprint_df %>%
  group_by(version, advert) %>%
  summarise(mean_predicted_PK = mean(predicted_PK))

ggplot(mean_predicted_values, aes(x = version, y = mean_predicted_PK, group = advert, color = advert)) +
  geom_point() +
  geom_line() +
  facet_wrap(~ advert) +
  labs(x = "Version Viewed (0 = no digital imprint)",
       y = "Mean Predicted PPI") +
  theme_minimal()

```

Below explores if the effect of the imprint on persuasion knowledge is impacted by the advert type.

```{r}

model <- lmer(PK ~ version * advert + (1 | id), data = imprint_df)

tab_model(model)

# Get predicted values
predicted_PK <- predict(model, newdata = imprint_df)

# Add predicted values to the data frame
imprint_df1 <- cbind(imprint_df, predicted_PK)

with(imprint_df1, interaction.plot(advert, version, predicted_PK,
                                  type = "b", pch = c(1, 16), 
                                  col = c("red", "blue"), 
                                  main = "Interaction Plot", 
                                  xlab = "Advert", 
                                  ylab = "Predicted PK"))


```

#### Supplementary: name recall with 

The effect of version is not found to be robust, when applying false discovery rate p-value corrections, suggesting it may vary between materials. This is checked below with a model that includes an interaction term between version and advert.

```{r, echo=FALSE}

#supplementary model 

recall_materials <- glmer(recall ~ version*Training.condition + version*advert + 
                           (1|id), 
               data = recall_df, 
               family = binomial(link = "logit"),
               control = glmerControl(optimizer = "bobyqa", 
                                            optCtrl = list(maxfun = 
                                                             1e5)))

#Bonferroni corrected multi-pair wise comparisons between adverts
library(emmeans)

# Get estimated marginal means (EMMs) for the interaction between version and advert
emm <- emmeans(recall_materials, ~ version|advert)

# Perform pairwise comparisons and get odds ratios
pairwise_or <- contrast(emm, "revpairwise", type = "response", adjust = "bonferroni")

#manual calculation of confidence intervals

# Extract the log odds ratios and standard errors
log_or_se <- as.data.frame(summary(pairwise_or))

# Calculate confidence intervals
log_or_se$lower.CL <- exp(log(log_or_se$odds.ratio) - 1.96 * log_or_se$SE)
log_or_se$upper.CL <- exp(log(log_or_se$odds.ratio) + 1.96 * log_or_se$SE)

# View the results with confidence intervals
log_or_se

#visualising the effect
# Get predicted values
predicted_recall <- predict(recall_materials, newdata = imprint_df)

# Add predicted values to the data frame
imprint_df1 <- cbind(imprint_df, predicted_recall)

with(imprint_df1, interaction.plot(advert, version, predicted_recall,
                                  type = "b", pch = c(1, 16), 
                                  col = c("red", "blue"), 
                                  main = "Interaction Plot", 
                                  xlab = "Advert", 
                                  ylab = "Predicted Recall"))

```

