---
title: "Supplementary Test Code"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains the code for the advert-level variations, which is included as a supplementary test to the main analysis. 


## Persuasion knowledge: interaction version*training model 

Showing the different levels of increase in persuasion knowledge across the different adverts, testing if there is an interaction effect?

```{r include=FALSE}

#plotting the random effects interaction for ainform_pk3

imprint_df$predicted_PK <- predict(ainform_pk3, re.form = NULL)

mean_predicted_values <- imprint_df %>%
  group_by(version, advert) %>%
  summarise(mean_predicted_PK = mean(predicted_PK))

ggplot(mean_predicted_values, aes(x = version, y = mean_predicted_PK, group = advert, color = advert)) +
  geom_point() +
  geom_line() +
  facet_wrap(~ advert) +
  labs(x = "Version Viewed (0 = no digital imprint)",
       y = "Mean Predicted PPI") +
  theme_minimal()

```

Below explores if the effect of the imprint on persuasion knowledge is impacted by the advert type.

```{r}

model <- lmer(PK ~ version * advert + (1 | id), data = imprint_df)

tab_model(model)

# Get predicted values
predicted_PK <- predict(model, newdata = imprint_df)

# Add predicted values to the data frame
imprint_df1 <- cbind(imprint_df, predicted_PK)

with(imprint_df1, interaction.plot(advert, version, predicted_PK,
                                  type = "b", pch = c(1, 16), 
                                  col = c("red", "blue"), 
                                  main = "Interaction Plot", 
                                  xlab = "Advert", 
                                  ylab = "Predicted PK"))


```

#### Supplementary: name recall with 

The effect of version is not found to be robust, when applying false discovery rate p-value corrections, suggesting it may vary between materials. This is checked below with a model that includes an interaction term between version and advert.

```{r, echo=FALSE}

#supplementary model 

recall_materials <- glmer(recall ~ version*Training.condition + version*advert + 
                           (1|id), 
               data = recall_df, 
               family = binomial(link = "logit"),
               control = glmerControl(optimizer = "bobyqa", 
                                            optCtrl = list(maxfun = 
                                                             1e5)))

#Bonferroni corrected multi-pair wise comparisons between adverts
library(emmeans)

# Get estimated marginal means (EMMs) for the interaction between version and advert
emm <- emmeans(recall_materials, ~ version|advert)

# Perform pairwise comparisons and get odds ratios
pairwise_or <- contrast(emm, "revpairwise", type = "response", adjust = "bonferroni")

#manual calculation of confidence intervals

# Extract the log odds ratios and standard errors
log_or_se <- as.data.frame(summary(pairwise_or))

# Calculate confidence intervals
log_or_se$lower.CL <- exp(log(log_or_se$odds.ratio) - 1.96 * log_or_se$SE)
log_or_se$upper.CL <- exp(log(log_or_se$odds.ratio) + 1.96 * log_or_se$SE)

# View the results with confidence intervals
log_or_se

#visualising the effect
# Get predicted values
predicted_recall <- predict(recall_materials, newdata = imprint_df)

# Add predicted values to the data frame
imprint_df1 <- cbind(imprint_df, predicted_recall)

with(imprint_df1, interaction.plot(advert, version, predicted_recall,
                                  type = "b", pch = c(1, 16), 
                                  col = c("red", "blue"), 
                                  main = "Interaction Plot", 
                                  xlab = "Advert", 
                                  ylab = "Predicted Recall"))

```

#### Supplementary analysis: advert level variations on informedness

Is there evidence to suggest that it is the aesthetic style and content of an advert itself that increases informedness about a source, and do digital imprints play a role in informing citizens above and beyond this?

Claims tested:

- Informedness about the source will be increased by the presence of a digital imprint, even when accounting for variations in campaign material content and format.

To further explore this, we can conduct an analysis comparing the effect of viewing each campaign post with and without the inclusion of a digital imprint on persuasion knowledge, political goal recognition, and perceived informedness.

```{r advert level variations in PK, echo=FALSE, fig.align='center'}

# Calculate summary statistics
summary_ad_PK <- imprint_df %>%
  group_by(advert, version) %>%
  summarise(n = n(),
            mean_pk = mean(PK, na.rm = TRUE),
            sd_pk = sd(PK, na.rm = TRUE),
            se_pk = sd_pk / sqrt(n),
            ci_upper = mean_pk + 1.96 * se_pk,
            ci_lower = mean_pk - 1.96 * se_pk) %>%
  ungroup()

kable(summary_ad_PK, format = "html", digits = 2, caption = "Decriptive bivariate statistics for percieved persuasion knowledge") %>%
  kable_classic(full_width = F, position = "center", html_font = "Cambria")

#Plotting the raw data

ad_PK_plot <- ggplot(data = imprint_df, aes(x = advert, y = PK, fill = version)) 

ad_PK_plot + 
  geom_point(aes(color = version), position = position_jitterdodge(), alpha = 0.5) +
  geom_boxplot(width = 0.2) +
  theme_minimal()

```

```{r advert level variations in PG, echo=FALSE, fig.align='center'}

# Calculate summary statistics
summary_ad_PG <- imprint_df %>%
  group_by(advert, version) %>%
  summarise(n = n(),
            mean_pg = mean(PG_value, na.rm = TRUE),
            sd_pg = sd(PG_value, na.rm = TRUE),
            se_pg = sd_pg / sqrt(n),
            ci_upper = mean_pg + 1.96 * se_pg,
            ci_lower = mean_pg - 1.96 * se_pg) %>%
  ungroup()

kable(summary_ad_PG, format = "html", digits = 2, caption = "Decriptive bivariate statistics for percieved political goal") %>%
  kable_classic(full_width = F, position = "center", html_font = "Cambria")

#Plotting the raw data

ad_PG_plot <- ggplot(data = imprint_df, aes(x = advert, y = PG_value, fill = version)) 

ad_PG_plot + 
  geom_point(aes(color = version), position = position_jitterdodge(), alpha = 0.5) +
  geom_boxplot(width = 0.2) +
  theme_minimal()

```

```{r advert level variations in informed, echo=FALSE, fig.align='center'}

# Calculate summary statistics
summary_ad_in <- imprint_df %>%
  group_by(advert, version) %>%
  summarise(n = n(),
            mean_in = mean(informed, na.rm = TRUE),
            sd_in = sd(informed, na.rm = TRUE),
            se_in = sd_in / sqrt(n),
            ci_upper = mean_in + 1.96 * se_in,
            ci_lower = mean_in - 1.96 * se_in) %>%
  ungroup()

kable(summary_ad_in, format = "html", digits = 2, caption = "Decriptive bivariate statistics for percieved informedness") %>%
  kable_classic(full_width = F, position = "center", html_font = "Cambria")

#Plotting the raw data

ad_in_plot <- ggplot(data = imprint_df, aes(x = advert, y = informed, fill = version))

ad_in_plot + 
  geom_point(aes(color = version), position = position_jitterdodge(), alpha = 0.5) +
  geom_boxplot(width = 0.2) +
  theme_minimal()

```


