---
title: "Disclosures and Third-Party Campaigns: Analysis Code"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    number_sections: true
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(lavaan)
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggeffects)
library(performance)
library(knitr)
library(kableExtra)
library(broom)
library(broom.mixed)
library(psych)
library(stats)
library(simr)

```

*This is the same document as analysis_script.Rmd', but knitted with corresponding outputs shown.*

This is the main analysis code for all models reported in the main paper, including the generation of effect sizes and equivalence testing. Please ensure you have the data frames 'mixedeffect_df.csv' and 'betweenmeasures_df.csv' downloaded from the OSF project. This code will look for these files in a folder named 'OSF_data'. Exclusions have already been applied to this dataset.

Alternatively, you can download 'main_data.csv' and use the 'main_datawrangle.Rmd' document to wrangle the data yourself, or to check the data processing code.

## Reading in the data files

This will use the here package.

```{r reading data}

mixedeffect_df <- read.csv(here("OSF_data", "mixedeffect_df.csv"))
betweenmeasure_df <- read.csv(here("OSF_data", "betweenmeasures_df.csv"))

```

## Randomisation checks

Below shows the successful randomisation across the training conditions (between measures).

```{r transforming variables, include=FALSE}

# converting demographic variables into factors for analysis

#gender, female as reference

gender_response_order <- c("Female", "Male", "Non-binary / third gender", "Prefer not to say")

betweenmeasure_df <- betweenmeasure_df %>%
  mutate(across(gender, ~factor(.x, levels = gender_response_order)))

#Education level, postgrad as reference

ed_response_order <- c("Postgraduate (e.g. M.Sc, Ph.D)", "Undergraduate University (e.g. BA, B.Sc, B.Ed)", "A-level, or equivalent", "GCSE level, or equivalent", "Other, please specify", "No formal qualifications")

betweenmeasure_df <- betweenmeasure_df %>%
  mutate(across(education, ~factor(.x, levels = ed_response_order)))

#partyID, Labour as reference

party_response_order <- c("Labour", "Conservative", "Liberal Democrat", "Reform UK", "United Kingdom Independence Party (UKIP)", "Green Party", "Scottish National Party (SNP)", "Plaid Cymru", "Sinn Féin", "Democratic Unionist Party", "Alliance Party", "Other, please specify___________", "I do not identify with any political party")

betweenmeasure_df <- betweenmeasure_df %>%
  mutate(across(partyID, ~factor(.x, levels = party_response_order)))

#ethnicity

ethnicity_response_order <- c("White", "Black", "Asian", "Mixed", "Other")

betweenmeasure_df <- betweenmeasure_df %>%
  mutate(across(Ethnicity.simplified, ~factor(.x, levels = ethnicity_response_order)))

# political interest

betweenmeasure_df$political_interest <- as.numeric(betweenmeasure_df$political_interest)

# age

betweenmeasure_df$age <- as.numeric(betweenmeasure_df$age)

```

```{r}

# Set up a results list
results <- list()

# Age (numerical)
tt_age <- t.test(age ~ Training.condition, data = betweenmeasure_df)
results[["Age"]] <- c(
  Test = "t-test",
  Statistic = round(tt_age$statistic, 2),
  df = round(tt_age$parameter, 2),
  p_value = round(tt_age$p.value, 3)
)

# Political interest (numerical)
tt_pi <- t.test(political_interest ~ Training.condition, data = betweenmeasure_df)
results[["Political interest"]] <- c(
  Test = "t-test",
  Statistic = round(tt_pi$statistic, 2),
  df = round(tt_pi$parameter, 2),
  p_value = round(tt_pi$p.value, 3)
)

# Gender (categorical, chi-squared)
tab_gender <- table(betweenmeasure_df$gender, betweenmeasure_df$Training.condition)
chi_gender <- chisq.test(tab_gender)
results[["Gender"]] <- c(
  Test = "Chi-squared",
  Statistic = round(chi_gender$statistic, 2),
  df = chi_gender$parameter,
  p_value = round(chi_gender$p.value, 3)
)

# Education (categorical, chi-squared)
tab_edu <- table(betweenmeasure_df$education, betweenmeasure_df$Training.condition)
chi_edu <- chisq.test(tab_edu)
results[["Education"]] <- c(
  Test = "Chi-squared",
  Statistic = round(chi_edu$statistic, 2),
  df = chi_edu$parameter,
  p_value = round(chi_edu$p.value, 3)
)

# Party ID (categorical, chi-squared)
tab_party <- table(betweenmeasure_df$partyID, betweenmeasure_df$Training.condition)
chi_party <- chisq.test(tab_party)
results[["Party ID"]] <- c(
  Test = "Chi-squared",
  Statistic = round(chi_party$statistic, 2),
  df = chi_party$parameter,
  p_value = round(chi_party$p.value, 3)
)

# Ethnicity (categorical, chi-squared)
tab_eth <- table(betweenmeasure_df$Ethnicity.simplified, betweenmeasure_df$Training.condition)
chi_eth <- chisq.test(tab_eth)
results[["Ethnicity"]] <- c(
  Test = "Chi-squared",
  Statistic = round(chi_eth$statistic, 2),
  df = chi_eth$parameter,
  p_value = round(chi_eth$p.value, 3)
)

# Convert to a data frame
results_df <- as.data.frame(do.call(rbind, results))

# Show table

kable(results_df, format = "latex", booktabs = TRUE,
      caption = "Randomisation Check Across Demographics") %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "striped"))

```

## Manipulation check

Below shows where in the ranking participants tended to rate 'voters' when asked who the digital imprint information was most useful for. 

```{r useful manipulation check, echo=FALSE}

#set as factor
betweenmeasure_df$useful_rank_1 <- as.factor(betweenmeasure_df$useful_rank_1)

betweenmeasure_df$useful_rank_1 <- factor(betweenmeasure_df$useful_rank_1, levels = c("6", "5", "4", "3", "2", "1"))

# Calculate the counts and percentages
useful_plot <- betweenmeasure_df %>%
  group_by(Training.condition, useful_rank_1) %>%
  summarise(Count = n()) %>%
  mutate(Percentage = (Count / sum(Count)) * 100)

#create plot

useful <- ggplot(useful_plot, aes(x = useful_rank_1, y = Count, fill = as.factor(Training.condition))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.5) +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_dodge(width = 0.6), 
           vjust = 0.5,
           hjust = -0.1,
            size = 3) +  # Add percentage labels above bars
  scale_fill_brewer(palette = "Paired",
                    labels = c("No Training", "Trained")) +
  labs(title = "Response option: 'Voters, to understand who is responsible for the campaign material'",
       x = "Rank Position",  
       y = "Count") +   
  facet_wrap(~ Training.condition, 
             labeller = labeller(Training.condition = c('0' = 'No Training', '1' = 'Training'))) +  # Facet labels
  theme_minimal() +
  theme(legend.position = "none",
        legend.title = element_blank(),
        title = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  coord_flip() +
  expand_limits(y = max(useful_plot$Count) * 1.1) +
  theme(aspect.ratio = 1/1.75)

useful

```

```{r wilcoxin signed rank, echo=FALSE}

# Wilcoxon signed-rank test for overall distribution of rank

betweenmeasure_df$useful_rank_1_num <- as.numeric(as.character(betweenmeasure_df$useful_rank_1))

wilcox.test(useful_rank_1_num ~ Training.condition, data = betweenmeasure_df, 
            alternative = "two.sided", exact = FALSE)

```

## A priori Statistical power

Sample size was in part constrained by financial considerations. A repeated measures design was adopted to increase statistical power. However, due to the novelty of this method in this empirical context, there was no clear parameters to harness within an apriori power calculation. 

An apriori power analysis was conducted based on our anticipated sample size of 1,250 and estimating hypothetical model parameters based on our expectations about variance and effect size. In the pre-registration, it was clarified that we expected a small effect size for the fixed effects of interest, this being the effect of viewing the digital imprint and the moderated interaction term between version and training (Cohens d = 0.10). To estimate the statistical power, we specified a mixed-effects model with random intercepts for participants (id) and adverts, assuming variances of 0.30 for each random effect and 0.60 for the residual error term. The corresponding fixed effects were set to produce small main and interaction effects (≈ d = 0.10, converted to raw units based on the total model variance). Simulated datasets were generated under these parameters using the simr package, and power was estimated for detecting the main and interaction effects with 500 Monte Carlo simulations at α = .05. 

Below uses the package simr to calculate the power the simulated models with the planned structure have to detect a main and interaction effect with an effect size of Cohens d = 0.10.

```{r power, eval=FALSE}

# Suppose 1,250 participants, each seeing 4 adverts
N <- 1250
design <- expand.grid(id = factor(seq_len(N)),
                      advert = factor(1:4))

# Between-subject factor (training)
set.seed(1)
id_level <- data.frame(id=levels(design$id),
                       Training.condition = sample(c(0,1), length(levels(design$id)), TRUE))
design <- merge(design, id_level, by="id", all.x=TRUE, sort=FALSE)

# Within subjects factor (version)
design$version <- rep(c(0,1), length.out = nrow(design))

# Hypothetical variances

var_id     <- 0.30      # Var of random intercept for id
var_advert <- 0.30      # Var of random intercept for advert
var_eps    <- 0.60      # Residual variance

# Convert variances to standard deviations

sd_id     <- sqrt(var_id)
sd_advert <- sqrt(var_advert)
sd_eps    <- sqrt(var_eps)

sd_total <- sqrt(var_id + var_advert + var_eps)  # convert d → raw units
small_d  <- 0.10
medium_d <- 0.20
small_raw <- small_d * sd_total  # ≈ raw effect size
medium_raw <- medium_d * sd_total

# Name fixed effects exactly as in your formula
fixefs <- c("(Intercept)" = 4.0,                   # plausible mean
            "version" = small_raw,                 # small main effect
            "Training.condition" = 0,              # no direct effect
            "version:Training.condition" = small_raw)  # small interaction

# Template model

sim_model <- makeLmer(
  Outcome ~ version * Training.condition + (1|id) + (1|advert),
  fixef   = fixefs,
  VarCorr = list(id = sd_id, advert = sd_advert),  # SDs for random effects
  sigma   = sd_eps,                                # residual SD 
  data    = design
)

# apriori for estimated N

# Main effect of version
powerSim(sim_model, test=fixed("version","t"), nsim=500)

# Interaction
powerSim(sim_model, test=fixed("version:Training.condition","t"), nsim=500)

```

## Reliability of aggregated scores

As there is few items for each scale, these models have very few degrees of freedom and are thus just identified. This produces some warnings to advise you that the omega hierachichal estimates will not be meaningful, only the omega total estimate. Omega total is reported in the paper.

```{r reliability, warning=FALSE}

# set scales

informed <- mixedeffect_df[, c("informed2_value", "informed3_value", "informed4_value")]
pk <- mixedeffect_df[, c("PK1_value", "PK2_value", "PK3_value", "PK4_value")]
credibility <- mixedeffect_df[, c("trustworthy_value", "accurate_value", "believable_value", "factual_value")]

# Perceived source identification
reliability_source <- psych::omega(informed, 1, plot = FALSE)
reliability_source$alpha
reliability_source$omega.tot

# Persuasion Knowledge
reliability_pk <- psych::omega(pk, 1, plot = FALSE)
reliability_pk$alpha
reliability_pk$omega.tot

# Credibility
reliability_cred <- psych::omega(credibility, 1, plot = FALSE)
reliability_cred$alpha
reliability_cred$omega.tot

```

## Group descriptives

```{r}

# univariate distributions

psych::describe(mixedeffect_df$informed)

psych::describe(mixedeffect_df$PK)

psych::describe(mixedeffect_df$credibility)

psych::describe(betweenmeasure_df$election_reg)

# Calculate means and standard deviations
descriptive_stats <- mixedeffect_df %>%
  group_by(Training.condition, version) %>%
  summarise(
    informed_mean = mean(informed, na.rm = TRUE),
    informed_sd = sd(informed, na.rm = TRUE),
    PK_mean = mean(PK, na.rm = TRUE),
    PK_sd = sd(PK, na.rm = TRUE),
    Credibility_mean = mean(credibility, na.rm = TRUE),
    Credibility_sd = sd(credibility, na.rm = TRUE),
    .groups = 'drop'
  )

# Create and format the table
descriptive_stats %>%
  kable(format = "latex", digits = 2,
        col.names = c("Training Condition","Version","Informed Mean","Informed SD",
                      "PK Mean","PK SD","Credibility Mean","Credibility SD"),
        booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("hold_position","striped"))

```

## Hypothesis Testing

Effect size calculation: 

Feingold, A. (2013). A regression framework for effect size assessments in longitudinal modeling of group differences. Review of General Psychology, 17(1), 111-121. https://pmc.ncbi.nlm.nih.gov/articles/PMC3743548/pdf/nihms489048.pdf

Piaskowski (2026) https://mirror.las.iastate.edu/CRAN/web/packages/emmeans/refman/emmeans.html

Lenth, R. V. (2016). Least-squares means: the R package lsmeans. Journal of statistical software, 69, 1-33. http://dx.doi.org/10.18637/jss.v069.i01 

“These results are consistent with the recent conclusion that “in certain situations (e.g., multilevel designs), no consensus exists on how to conceptualize and/or calculate effect size measures” (APA Publications and Communications Board Working Group on Journal Article Reporting Standards, 2008, p. 850).” (Feingold, 2013, p.3)

In mixed-effect modelling, the appropriateness of using Cohens d is debated as there are multiple sources of variation that are challenging to account for. Below shows how the emmeans eff_size() function is used to estimate Cohen's d, and the assumptions employed in the estimation (see Piaskowski, 2026).

```{r}

# ready the variables for analysis

mixedeffect_df <- mixedeffect_df %>%
  mutate(
    version = factor(version, levels = c(0, 1)),
    Training.condition = factor(Training.condition, levels = c(0, 1))
  )

```

### H1: Persuasion knowledge

```{r H1, echo=FALSE, fig.align='center', warning=FALSE}

pk_mod <- lmer(PK ~ version + Training.condition + (1 | id) + (1|advert), data = mixedeffect_df, control = lmerControl(optimizer = "bobyqa"))

summary(pk_mod)

# 95% confidence intervals 

confint(pk_mod)

# Calculating effect sizes through standardised coeffecients

# estimated effect size of version, averaged over both training conditions

emm_version <- emmeans(pk_mod, ~ version)

cd_version_pk <- eff_size(
  emm_version,
  sigma = sigma(pk_mod), # Sigma is the model’s residual standard deviation, capturing within-unit variability
  edf = Inf, #edf = 'effective degrees of freedom' for sigma, which is treated as known (Inf) due to the large sample size
  method = "pairwise"
)

# reveals a negative number for the effect size because the mean of imprint effects is larger than the mean of no-imprint effects (and it calculates it as control - imprint). Reported as positive numbers in the paper.

cd_version_pk

```
 
### H2: Perceived source clarification

```{r H2, echo=FALSE, warning=FALSE}

# run model

inform_int <- lmer(informed ~ version*Training.condition + (1 | id) + (1|advert), data = mixedeffect_df)

summary(inform_int)

# 95% confidence intervals 

confint(inform_int)

# Calculating effect sizes through standardised coeffecients

# estimated effect size of version, averaged over both training conditions

emm_version <- emmeans(inform_int, ~ version)

cd_version_inform <- eff_size(
  emm_version,
  sigma = sigma(inform_int), # Sigma is the model’s residual standard deviation, capturing within-unit variability
  edf = Inf, #edf = 'effective degrees of freedom' for sigma, which is treated as known (Inf) due to the large sample size
  method = "pairwise"
)

cd_version_inform

# estimated effect sizes for version within each training condition for the interaction term

emm_inform_int <- emmeans(inform_int, ~ version | Training.condition)

cd_int_inform <- eff_size(
  emm_inform_int,
  sigma = sigma(inform_int),
  edf = Inf,          
  method = "pairwise"
)

cd_int_inform


```

#### Figure 1

```{r figure 1, echo=FALSE, fig.align='center'}

# plot

inform_preds <- ggeffects::ggpredict(inform_int, terms = c("Training.condition", "version"))

# Set the dodge width 
dodge_width <- 0.3  

inform_interaction <- ggplot2::ggplot(inform_preds, aes(x = x, y = predicted, color = group)) +
  geom_point(position = position_dodge(width = dodge_width), size = 3) +  
  geom_line(aes(group = group), position = position_dodge(width = dodge_width), linewidth = 1) +  # Lines with dodge
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                position = position_dodge(width = dodge_width), width = 0.1) +  # Error bars with dodge
  scale_color_manual(values = c("0" = "#4682B4", "1" = "#800020"), 
                     labels = c("Digital Imprint Absent", "Digital Imprint Viewed")) +
  scale_x_discrete(labels = c("0" = "Not trained", "1" = "Trained")) +
  labs(x = "Training Condition", 
       y = "Predicted Score (95% CI)",
       title = "") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 12))

inform_interaction

```

### H3: Confidence in regulation

```{r H3, echo=FALSE}

# Welch's t-test (unequal variances) 
welch <- t.test(election_reg ~ Training.condition,
                data = betweenmeasure_df,
                var.equal = FALSE,    # Welch 
                conf.level = 0.95,
                na.action = na.omit)
welch

# cohens d

effectsize::cohens_d(election_reg ~ Training.condition, data = betweenmeasure_df)

# Group descriptives
desc <- betweenmeasure_df %>%
  filter(!is.na(election_reg), !is.na(Training.condition)) %>%
  group_by(Training.condition) %>%
  summarise(n = n(), m = mean(election_reg), sd = sd(election_reg), .groups = "drop") %>%
  arrange(Training.condition)

m0  <- desc$m[1];  sd0 <- desc$sd[1];  n0 <- desc$n[1]
m1  <- desc$m[2];  sd1 <- desc$sd[2];  n1 <- desc$n[2]

```
### H4: Perceieved credibility

```{r H4, echo=FALSE, fig.align='center'}

cred_int <- lmer(credibility ~ version*Training.condition + (1 | id) + (1|advert), data = mixedeffect_df)

summary(cred_int)

# 95% confidence intervals 

confint(cred_int)

# interaction plotted

cred_preds <- ggeffects::ggpredict(cred_int, terms = c("Training.condition", "version"))

cred_interaction <- ggplot2::ggplot(cred_preds, aes(x = x, y = predicted, color = group)) +
  geom_point(position = position_dodge(width = dodge_width), size = 3) +  
  geom_line(aes(group = group), position = position_dodge(width = dodge_width), linewidth = 1) +  # Lines with dodge
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                position = position_dodge(width = dodge_width), width = 0.1) +  # Error bars with dodge
  scale_color_manual(values = c("0" = "#4682B4", "1" = "#800020"), 
                     labels = c("Digital Imprint Absent", "Digital Imprint Viewed")) +
  scale_x_discrete(labels = c("0" = "Not trained", "1" = "Trained")) +
  labs(x = "Training Condition", 
       y = "Predicted Score (95% CI)",
       title = "") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 12))

cred_interaction

```

#### Mixed Model Assumptions

```{r eval=FALSE}

performance::check_model(inform_int)
performance::check_model(pk_int)
performance::check_model(cred_int)

```

### Exploratory SEM

Below shows the code used to process the data and build the multi-level SEM using lavaan.

```{r parellel mediation model}

df <- mixedeffect_df

# Descriptive correlations 

vars <- c(
  "informed2_value","informed3_value","informed4_value",
  "PK1_value","PK2_value","PK3_value","PK4_value",
  "accurate_value","trustworthy_value","believable_value","factual_value"
)

df_between <- df %>%
  group_by(id) %>%
  summarise(across(all_of(vars), ~mean(.x, na.rm=TRUE)), .groups="drop")

cor_between <- cor(df_between[vars], use = "pairwise.complete.obs")

sd_between <- sapply(df_between[vars], function(x) sd(x, na.rm = TRUE))
sd_between

cor_between
sd_between

df_within <- df %>%
  group_by(id) %>%
  mutate(across(all_of(vars), ~ .x - mean(.x, na.rm=TRUE))) %>%
  ungroup()

cor_within <- cor(df_within[vars], use = "pairwise.complete.obs")

cor_within

```

#### SEM descriptives table

```{r echo=FALSE}

# ensure variables are numeric
df <- df %>%
  mutate(across(all_of(vars), ~ suppressWarnings(as.numeric(.x))))

df_between <- df %>%
  group_by(id) %>%
  summarise(across(all_of(vars), ~ mean(.x, na.rm = TRUE)), .groups = "drop")

# Between: mean of person means
mean_between <- sapply(df_between[vars], function(x) mean(x, na.rm = TRUE))

# Between: sd of person means
sd_between   <- sapply(df_between[vars], function(x) sd(x, na.rm = TRUE))

# Within: person-mean–centered scores (pooled across rows)
df_within <- df %>%
  group_by(id) %>%
  mutate(across(all_of(vars), ~ .x - mean(.x, na.rm = TRUE))) %>%
  ungroup()

# Within: sd of centered values pooled across all rows
sd_within <- sapply(df_within[vars], function(x) sd(x, na.rm = TRUE))

# ICC per item from empty random-intercept models
get_icc <- function(y, id) {
  d <- data.frame(y = y, id = id)
  d <- d[!is.na(d$y) & !is.na(d$id), ]
  if (length(unique(d$id)) < 2) return(NA_real_)      # need >= 2 clusters
  # need some within-cluster variance
  wsd <- tapply(d$y, d$id, function(x) sd(x, na.rm = TRUE))
  if (all(is.na(wsd)) || all(wsd %in% c(0, NA))) return(NA_real_)
  m <- lmer(y ~ 1 + (1|id), data = d, REML = TRUE,
            control = lmerControl(check.nobs.vs.nRE = "ignore",
                                  check.nobs.vs.nlev = "ignore",
                                  check.nobs.vs.rankZ = "ignore"))
  vc <- as.data.frame(VarCorr(m))
  tau2   <- vc$vcov[vc$grp == "id"]        # between
  sigma2 <- vc$vcov[vc$grp == "Residual"]  # within
  as.numeric(tau2 / (tau2 + sigma2))
}

icc_vals <- sapply(vars, function(v) get_icc(df[[v]], df$id))

# Create and format table
appendix_tbl <- tibble(
  Variable       = vars,
  `Mean (Between)` = as.numeric(mean_between[vars]),
  `SD (Between)`   = as.numeric(sd_between[vars]),
  `SD (Within)`    = as.numeric(sd_within[vars]),
  ICC              = as.numeric(icc_vals[vars])
) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))

appendix_tbl

```

```{r multilevel SEM}

# Reported multi-level SEM

model <- '
  level: 1
    # Within (L1) measurement
    Informed_w =~ informed2_value + informed3_value + informed4_value
    PK_w       =~ PK1_value + PK3_value 
    Cred_w     =~ accurate_value + trustworthy_value + believable_value + factual_value

    # Within (L1) structural
    Informed_w ~ a1*version
    PK_w       ~ a2*version
    Cred_w     ~ b1*Informed_w + b2*PK_w + cprime*version

    # Defined (within-level) effects
    ind_Informed := a1*b1
    ind_PK       := a2*b2
    ind_total    := ind_Informed + ind_PK
    total        := cprime + ind_total

  level: 2
    Informed_b =~ informed2_value + informed3_value + informed4_value
    PK_b       =~ PK1_value + PK3_value
    Cred_b     =~ accurate_value + trustworthy_value + believable_value + factual_value
    
    Informed_b ~ Training.condition
    PK_b       ~ Training.condition
    Cred_b     ~ Training.condition
'

fit <- sem(model, data=df, cluster="id", estimator="MLR", std.lv=TRUE, meanstructure=TRUE, fixed.x=TRUE)

summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)

```

### Assumptions for MLE models

- Functional form (linearity), fitted vs residual
- Homogeneity of variance, scale location plot
- Normality of level-1 residuals, Q-Q plot
- Normality of random effects, Q-Q plot
- Level-2 leverage points 

```{r level one assumptions}

library(lme4)
library(ggplot2)
library(patchwork)

# 3-panel diagnostic for an lmer model
diag_lmer <- function(fit, model_title = "Model", save_path = NULL) {
  # data for plots
  df <- data.frame(
    fitted  = fitted(fit),                          # conditional fitted values (incl. RE)
    sresid  = resid(fit, type = "pearson")          # Pearson residuals (≈ standardized)
  )
  df$resid <- resid(fit, type = "response")

  # A) Residuals vs Fitted (functional form)
  pA <- ggplot(df, aes(fitted, resid)) +
    geom_point(shape = 16, alpha = 0.6) +
    geom_smooth(method = "loess", se = FALSE, linewidth = 0.4) +
    geom_hline(yintercept = 0, linetype = 2) +
    labs(x = "Fitted values (conditional)", y = "Residuals",
         title = paste(model_title, "Functional Form Check (Residuals vs Fitted)")) +
    theme_bw(base_size = 11)

  # B) Scale–Location (homoscedasticity)
  pB <- ggplot(df, aes(fitted, sqrt(abs(sresid)))) +
    geom_point(shape = 16, alpha = 0.6) +
    geom_smooth(method = "loess", se = FALSE, linewidth = 0.4) +
    labs(x = "Fitted values (conditional)",
         y = expression(sqrt("|Pearson residuals|")),
         title = paste(model_title, "Level-1: Homoskedasticity Check (Scale–Location)")) +
    theme_bw(base_size = 11)

  # C) Normal Q–Q (of Pearson residuals)
  qq <- qqnorm(df$sresid, plot.it = FALSE)
  qq_df <- data.frame(theoretical = qq$x, sample = qq$y)

  pC <- ggplot(qq_df, aes(theoretical, sample)) +
    geom_point(shape = 16, alpha = 0.6) +
    geom_abline(intercept = 0, slope = 1, linetype = 2) +
    labs(x = "Theoretical Quantiles", y = "Sample Quantiles",
         title = paste(model_title, "Level-1: Normality Check (Normal Q–Q)")) +
    theme_bw(base_size = 11)

  # combine vertically
  p <- (pA / pB / pC) +
    plot_annotation(
      title = paste(model_title, ": Inspecting Mixed-Model Assumptions"),
      subtitle = deparse(formula(fit)),
      tag_levels = "A"
    ) &
    theme(plot.title = element_text(size = 12),
          plot.subtitle = element_text(size = 9))

  if (!is.null(save_path)) {
    ggsave(save_path, plot = p, width = 8.27, height = 11.69, units = "in", dpi = 300)
  }
  p
}

# Apply

diag_lmer(pk_mod, model_title = "Hypothesis 1: Persuasion Knowledge", save_path = "assumptions/pk_lmer_diagnostics.png")

diag_lmer(inform_int, model_title = "Hypothesis 2: Source Identification", save_path = "assumptions/sourceid_lmer_diagnostics.png")

diag_lmer(cred_int, model_title = "Hypothesis 4: Perceived Credibility", save_path = "assumptions/credibility_lmer_diagnostics.png")

```

### Level-2 assumptions (residuals and leverage)

```{r persuasion knowledge level two assumptions}

# Cook's D with influence.ME

infl_pk_advert <- influence(pk_mod, group = "advert")

cd <- cooks.distance(infl_pk_advert)

# With 4 adverts, this will be 4 / 4 = 1
thr <- 4 / length(cd)

sum(cd > thr)

cd_df <- data.frame(
  advert = factor(seq_along(cd)),
  cooksD = as.numeric(cd)
)

pk_cook_l2 <- ggplot(cd_df, aes(x = advert, y = cooksD)) +
  geom_col(fill = "black", alpha = 0.7) +
  geom_hline(
    yintercept = thr,
    color = "red3",
    linetype = "dashed",
    linewidth = 0.8
  ) +
  labs(
    title = "Cook's D by experimental stimulus",
    x = "Experimental stimulus",
    y = paste0("Cook's distance (red line = ", round(thr, 3), ")")
  ) +
  theme_bw(base_size = 12)

# Q-Q plot of standardised advert random effects

ran_pk <- ranef(pk_mod, condVar = TRUE)

# Extract advert-level random intercepts
re_advert <- ran_pk[["advert"]]

# Extract posterior variances for advert random effects
postVar_advert <- attr(re_advert, "postVar")

# Standardised random intercepts
z_b <- as.numeric(re_advert[[1]] / sqrt(postVar_advert[1, 1, ]))

qq_df <- data.frame(
  advert = rownames(re_advert),
  z_b = z_b
)

pk_qq_l2 <- ggplot(qq_df, aes(sample = z_b)) +
  stat_qq(shape = 16) +
  stat_qq_line(linetype = 2, alpha = 0.6) +
  labs(
    title = "Q-Q Plot of Standardised Advert-Level Random Effects",
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_bw(base_size = 12)

# Combine plots

pk_l2_diagnostics_advert <- (pk_qq_l2 / pk_cook_l2) +
  plot_annotation(
    title = "Level-2 Diagnostics for Persuasion Knowledge Model",
    subtitle = "A: Normality of Advert Random Effects | B: Cluster Influence (Cook's D)",
    tag_levels = "A"
  ) &
  theme(
    plot.title = element_text(size = 13, face = "bold"),
    plot.subtitle = element_text(size = 10),
    plot.tag = element_text(size = 12, face = "bold")
  )

pk_l2_diagnostics_advert

# save

ggsave(
  filename = file.path(
    "C:/Users/pcq21hcg/Documents/digitalimprints_experiment",
    "assumptions",
    "pk_L2_advert.png"
  ),
  plot = pk_l2_diagnostics_advert,
  width = 8.27,
  height = 9,
  units = "in",
  dpi = 300
)

```

```{r perceived source identification level two assumptions}

# Cook's D with influence.ME

infl_inform_advert <- influence(inform_int, group = "advert")

cd <- cooks.distance(infl_inform_advert)

# With 4 adverts, this will be 4 / 4 = 1
thr <- 4 / length(cd)

sum(cd > thr)

cd_df <- data.frame(
  advert = factor(seq_along(cd)),
  cooksD = as.numeric(cd)
)

inform_cook_l2 <- ggplot(cd_df, aes(x = advert, y = cooksD)) +
  geom_col(fill = "black", alpha = 0.7) +
  geom_hline(
    yintercept = thr,
    color = "red3",
    linetype = "dashed",
    linewidth = 0.8
  ) +
  labs(
    title = "Cook's D by experimental stimulus",
    x = "Experimental stimulus",
    y = paste0("Cook's distance (red line = ", round(thr, 3), ")")
  ) +
  theme_bw(base_size = 12)

# Q-Q plot of standardised advert random effects

ran_inform <- ranef(inform_int, condVar = TRUE)

# Extract advert-level random intercepts
re_advert <- ran_inform[["advert"]]

# Extract posterior variances for advert random effects
postVar_advert <- attr(re_advert, "postVar")

# Standardised random intercepts
z_b <- as.numeric(re_advert[[1]] / sqrt(postVar_advert[1, 1, ]))

qq_df <- data.frame(
  advert = rownames(re_advert),
  z_b = z_b
)

inform_qq_l2 <- ggplot(qq_df, aes(sample = z_b)) +
  stat_qq(shape = 16) +
  stat_qq_line(linetype = 2, alpha = 0.6) +
  labs(
    title = "Q-Q Plot of Standardised Advert-Level Random Effects",
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_bw(base_size = 12)

# Combine plots

inform_l2_diagnostics_advert <- (inform_qq_l2 / inform_cook_l2) +
  plot_annotation(
    title = "Level-2 Diagnostics for Perceived Source Identification Model",
    subtitle = "A: Normality of Advert Random Effects | B: Cluster Influence (Cook's D)",
    tag_levels = "A"
  ) &
  theme(
    plot.title = element_text(size = 13, face = "bold"),
    plot.subtitle = element_text(size = 10),
    plot.tag = element_text(size = 12, face = "bold")
  )

inform_l2_diagnostics_advert

# save

ggsave(
  filename = file.path(
    "C:/Users/pcq21hcg/Documents/digitalimprints_experiment",
    "assumptions",
    "inform_L2_advert.png"
  ),
  plot = inform_l2_diagnostics_advert,
  width = 8.27,
  height = 9,
  units = "in",
  dpi = 300
)

```

```{r perceived credibility level two assumptions}

# Cook's D with influence.ME

infl_cred_advert <- influence(cred_int, group = "advert")

cd <- cooks.distance(infl_cred_advert)

# With 4 adverts, this will be 4 / 4 = 1
thr <- 4 / length(cd)

sum(cd > thr)

cd_df <- data.frame(
  advert = factor(seq_along(cd)),
  cooksD = as.numeric(cd)
)

cred_cook_l2 <- ggplot(cd_df, aes(x = advert, y = cooksD)) +
  geom_col(fill = "black", alpha = 0.7) +
  geom_hline(
    yintercept = thr,
    color = "red3",
    linetype = "dashed",
    linewidth = 0.8
  ) +
  labs(
    title = "Cook's D by experimental stimulus",
    x = "Experimental stimulus",
    y = paste0("Cook's distance (red line = ", round(thr, 3), ")")
  ) +
  theme_bw(base_size = 12)

# Q-Q plot of standardised advert random effects

ran_cred <- ranef(cred_int, condVar = TRUE)

# Extract advert-level random intercepts
re_advert <- ran_cred[["advert"]]

# Extract posterior variances for advert random effects
postVar_advert <- attr(re_advert, "postVar")

# Standardised random intercepts
z_b <- as.numeric(re_advert[[1]] / sqrt(postVar_advert[1, 1, ]))

qq_df <- data.frame(
  advert = rownames(re_advert),
  z_b = z_b
)

cred_qq_l2 <- ggplot(qq_df, aes(sample = z_b)) +
  stat_qq(shape = 16) +
  stat_qq_line(linetype = 2, alpha = 0.6) +
  labs(
    title = "Q-Q Plot of Standardised Advert-Level Random Effects",
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_bw(base_size = 12)

# Combine plots

cred_l2_diagnostics_advert <- (cred_qq_l2 / cred_cook_l2) +
  plot_annotation(
    title = "Level-2 Diagnostics for Perceived Credibility Model",
    subtitle = "A: Normality of Advert Random Effects | B: Cluster Influence (Cook's D)",
    tag_levels = "A"
  ) &
  theme(
    plot.title = element_text(size = 13, face = "bold"),
    plot.subtitle = element_text(size = 10),
    plot.tag = element_text(size = 12, face = "bold")
  )

cred_l2_diagnostics_advert

# save

ggsave(
  filename = file.path(
    "C:/Users/pcq21hcg/Documents/digitalimprints_experiment",
    "assumptions",
    "cred_L2_advert.png"
  ),
  plot = cred_l2_diagnostics_advert,
  width = 8.27,
  height = 9,
  units = "in",
  dpi = 300
)

```

#### More meaningful plot that Cooks d with only 4 stimuli

This is a descriptive way to assess the contribution each advert is having and to see the variation. It cannot tell you what is a leverage point, but indicates non-uniformity across the adverts.

```{r remove one advert plot persuasion knowledge}

full_fixed <- data.frame(
  term = names(fixef(pk_mod)),
  full_model = as.numeric(fixef(pk_mod))
)

loo_fixed_long <- infl_pk_advert$`fixed.effects[-advert]` %>%
  as.data.frame() %>%
  tibble::rownames_to_column("removed_advert") %>%
  pivot_longer(
    cols = -removed_advert,
    names_to = "term",
    values_to = "estimate"
  )

# change labels in plot

loo_fixed_long <- loo_fixed_long %>%
  mutate(
    term_label = dplyr::recode(
      term,
      "(Intercept)" = "Intercept",
      "Training.condition1" = "Training",
      "version1" = "Version",
      "version1:Training.condition1" = "Version × Training"
    )
  )

# plot

fixedef_pk <- ggplot(loo_fixed_long, aes(x = removed_advert, y = estimate)) +
  geom_point(size = 2) +
  geom_hline(
    data = full_fixed %>%
      mutate(
        term_label = dplyr::recode(
          term,
          "(Intercept)" = "Intercept",
          "Training.condition1" = "Training",
          "version1" = "Version",
          "version1:Training.condition1" = "Version × Training"
        )
      ),
    aes(yintercept = full_model),
    linetype = "dashed",
    colour = "red"
  ) +
  facet_wrap(~ term_label, scales = "free_y") +
  labs(
    title = "Changes to fixed-effect estimates when each advert is removed (persuasion knowledge)",
    x = "Advert removed",
    y = "Fixed-effect estimate",
    caption = "Dashed red line shows the full-model estimate."
  ) +
  theme_bw()

# save

ggsave(
  filename = file.path(
    "C:/Users/pcq21hcg/Documents/digitalimprints_experiment",
    "assumptions",
    "fixedef_L2_pk.png"
  ),
  plot = fixedef_pk,
  width = 8.27,
  height = 3,
  units = "in",
  dpi = 300
)

```

```{r remove one advert plot inform}

full_fixed <- data.frame(
  term = names(fixef(inform_int)),
  full_model = as.numeric(fixef(inform_int))
)

loo_fixed_long <- infl_inform_advert$`fixed.effects[-advert]` %>%
  as.data.frame() %>%
  tibble::rownames_to_column("removed_advert") %>%
  pivot_longer(
    cols = -removed_advert,
    names_to = "term",
    values_to = "estimate"
  )

# change labels in plot

loo_fixed_long <- loo_fixed_long %>%
  mutate(
    term_label = dplyr::recode(
      term,
      "(Intercept)" = "Intercept",
      "Training.condition1" = "Training",
      "version1" = "Version",
      "version1:Training.condition1" = "Version × Training"
    )
  )

# plot

fixedef_inform <- ggplot(loo_fixed_long, aes(x = removed_advert, y = estimate)) +
  geom_point(size = 2) +
  geom_hline(
    data = full_fixed %>%
      mutate(
        term_label = dplyr::recode(
          term,
          "(Intercept)" = "Intercept",
          "Training.condition1" = "Training",
          "version1" = "Version",
          "version1:Training.condition1" = "Version × Training"
        )
      ),
    aes(yintercept = full_model),
    linetype = "dashed",
    colour = "red"
  ) +
  facet_wrap(~ term_label, scales = "free_y") +
  labs(
    title = "Changes to fixed-effect estimates when each advert is removed (source identification)",
    x = "Advert removed",
    y = "Fixed-effect estimate",
    caption = "Dashed red line shows the full-model estimate."
  ) +
  theme_bw()

# save

ggsave(
  filename = file.path(
    "C:/Users/pcq21hcg/Documents/digitalimprints_experiment",
    "assumptions",
    "fixedef_L2_inform.png"
  ),
  plot = fixedef_inform,
  width = 8.27,
  height = 5,
  units = "in",
  dpi = 300
)

```

```{r remove one advert plot cred}

full_fixed <- data.frame(
  term = names(fixef(cred_int)),
  full_model = as.numeric(fixef(cred_int))
)

loo_fixed_long <- infl_cred_advert$`fixed.effects[-advert]` %>%
  as.data.frame() %>%
  tibble::rownames_to_column("removed_advert") %>%
  pivot_longer(
    cols = -removed_advert,
    names_to = "term",
    values_to = "estimate"
  )

# Label dictionary: includes both possible naming styles
term_labels <- c(
  "(Intercept)" = "Intercept",
  "Training.condition1" = "Training",
  "Training.condition" = "Training",
  "version1" = "Version",
  "version" = "Version",
  "version1:Training.condition1" = "Version × Training",
  "version:Training.condition" = "Version × Training",
  "version1:Training.condition" = "Version × Training",
  "version:Training.condition1" = "Version × Training"
)

# Apply labels to leave-one-out estimates
loo_fixed_long <- loo_fixed_long %>%
  mutate(
    term_label = dplyr::recode(term, !!!term_labels),
    term_label = factor(
      term_label,
      levels = c("Intercept", "Version", "Training", "Version × Training")
    )
  )

# Apply labels to full-model estimates
full_fixed <- full_fixed %>%
  mutate(
    term_label = dplyr::recode(term, !!!term_labels),
    term_label = factor(
      term_label,
      levels = c("Intercept", "Version", "Training", "Version × Training")
    )
  )

# Plot
fixedef_cred <- ggplot(loo_fixed_long, aes(x = removed_advert, y = estimate)) +
  geom_point(size = 2) +
  geom_hline(
    data = full_fixed,
    aes(yintercept = full_model),
    linetype = "dashed",
    colour = "red"
  ) +
  facet_wrap(~ term_label, scales = "free_y") +
  labs(
    title = "Changes to fixed-effect estimates when each advert is removed (credibility)",
    x = "Advert removed",
    y = "Fixed-effect estimate",
    caption = "Dashed red line shows the full-model estimate."
  ) +
  theme_bw()

ggsave(
  filename = file.path(
    "C:/Users/pcq21hcg/Documents/digitalimprints_experiment",
    "assumptions",
    "fixedef_L2_cred.png"
  ),
  plot = fixedef_cred,
  width = 8.27,
  height = 5,
  units = "in",
  dpi = 300
)


```


### Participant-level

```{r source identification level two assumptions participant}

# Cook's D with influence.ME

infl_inf <- influence(inform_int, group = "id")  # cluster-level influence object
cd   <- cooks.distance(infl_inf)             # Cook’s D per cluster (id)
thr  <- 4/length(cd)                       # heuristic cutoff
sum(cd > thr) 

cd_df <- data.frame(
  id = 1:length(cd),
  cooksD = cd
)

inf_cook_l2 <- ggplot(cd_df, aes(x = id, y = cooksD)) +
  geom_col(fill = "black", alpha = 0.7) +
  geom_hline(yintercept = thr, color = "red3", linetype = "dashed", linewidth = 0.8) +
  labs(
    title = "Cook's D by cluster",
    x = "Cluster index (id)",
    y = "Cook's distance (red line = 0.003)"
  ) +
  theme_bw(base_size = 12)

# Q-Q plot of residuals

# Standardised random intercepts (z_b)
re <- ranef(inform_int, condVar = TRUE)$id
postVar <- attr(ranef(inform_int, condVar = TRUE)[[1]], "postVar")
z_b <- as.numeric(re[[1]] / sqrt(postVar[1, 1, ]))

# Q–Q plot
inf_qq_l2 <- ggplot(data.frame(z_b = z_b), aes(sample = z_b)) +
  stat_qq(shape = 16) +
  stat_qq_line(linetype = 2, alpha = 0.6) +
  labs(
    title = "Q–Q Plot of Standardised Level-2 Random Effects",
    x = "Theoretical Quantiles", y = "Sample Quantiles"
  ) +
  theme_bw(base_size = 12)

# Combine the two plots vertically with patchwork
inf_l2_diagnostics <- (inf_qq_l2 / inf_cook_l2) +
  plot_annotation(
    title = "Level-2 Diagnostics for Perc. Source Identification Model",
    subtitle = "A: Normality of Random Effects   |   B: Cluster Influence (Cook’s D)",
    tag_levels = "A"   # labels them A, B automatically
  ) &
  theme(
    plot.title = element_text(size = 13, face = "bold"),
    plot.subtitle = element_text(size = 10),
    plot.tag = element_text(size = 12, face = "bold")
  )

ggsave(
  filename = "assumptions/inform_L2_diagnostics.png",
  plot = inf_l2_diagnostics,
  width = 8.27,    # A4 width in inches
  height = 9,  # A4 height in inches
  units = "in",
  dpi = 300
)

```

```{r credibility level two assumptions}

# Cook's D with influence.ME

infl_cred <- influence(cred_int, group = "id")  # cluster-level influence object
cd   <- cooks.distance(infl_cred)             # Cook’s D per cluster (id)
thr  <- 4/length(cd)                       # heuristic cutoff
sum(cd > thr) 

cd_df <- data.frame(
  id = 1:length(cd),
  cooksD = cd
)

cred_cook_l2 <- ggplot(cd_df, aes(x = id, y = cooksD)) +
  geom_col(fill = "black", alpha = 0.7) +
  geom_hline(yintercept = thr, color = "red3", linetype = "dashed", linewidth = 0.8) +
  labs(
    title = "Cook's D by cluster",
    x = "Cluster index (id)",
    y = "Cook's distance (red line = 0.003)"
  ) +
  theme_bw(base_size = 12)

# Q-Q plot of residuals

# Standardised random intercepts (z_b)
re <- ranef(cred_int, condVar = TRUE)$id
postVar <- attr(ranef(cred_int, condVar = TRUE)[[1]], "postVar")
z_b <- as.numeric(re[[1]] / sqrt(postVar[1, 1, ]))

# Q–Q plot
cred_qq_l2 <- ggplot(data.frame(z_b = z_b), aes(sample = z_b)) +
  stat_qq(shape = 16) +
  stat_qq_line(linetype = 2, alpha = 0.6) +
  labs(
    title = "Q–Q Plot of Standardised Level-2 Random Effects",
    x = "Theoretical Quantiles", y = "Sample Quantiles"
  ) +
  theme_bw(base_size = 12)

# Combine the two plots vertically with patchwork
cred_l2_diagnostics <- (cred_qq_l2 / cred_cook_l2) +
  plot_annotation(
    title = "Level-2 Diagnostics for Perc. Credibility Model",
    subtitle = "A: Normality of Random Effects   |   B: Cluster Influence (Cook’s D)",
    tag_levels = "A"   # labels them A, B automatically
  ) &
  theme(
    plot.title = element_text(size = 13, face = "bold"),
    plot.subtitle = element_text(size = 10),
    plot.tag = element_text(size = 12, face = "bold")
  )

ggsave(
  filename = "assumptions/cred_L2_diagnostics.png",
  plot = cred_l2_diagnostics,
  width = 8.27,    # A4 width in inches
  height = 9,  # A4 height in inches
  units = "in",
  dpi = 300
)

```

### Assumptions for Welches t-test

```{r assumptions for H3}

welch_df <- betweenmeasure_df %>%
  select(election_reg, Training.condition) %>%
  filter(!is.na(election_reg), !is.na(Training.condition)) %>%
  mutate(Training.condition = as.factor(Training.condition))

# check for approx normality within groups

welches_dist <- ggplot(welch_df, aes(x = election_reg)) +
  geom_histogram(bins = 20) +
  facet_wrap(~ Training.condition) +
  labs(
    x = "Confidence in Regulation",
    y = "Count"
  )

# normality

welches_normality <- ggplot(welch_df, aes(sample = election_reg)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~ Training.condition) +
  labs(
    x = "Theoretical quantiles",
    y = "Sample quantiles"
  )

# save

ggsave(
  filename = file.path(
    "C:/Users/pcq21hcg/Documents/digitalimprints_experiment",
    "assumptions",
    "assumption_welches_normality.png"
  ),
  plot = welches_normality,
  width = 8.27,
  height = 5,
  units = "in",
  dpi = 300
)

```


# Robustness checks

Bootstrapped confidence intervals best for skewed distributions.

```{r}

# Persuasion Knowledge

pk_boot_ci <- confint(
  pk_mod,
  method = "boot",
  nsim = 1000,
  parm = "beta_",
  oldNames = FALSE
)

pk_boot_ci

# informed

# Persuasion Knowledge

inform_boot_ci <- confint(
  inform_int,
  method = "boot",
  nsim = 1000,
  parm = "beta_",
  oldNames = FALSE
)

inform_boot_ci

# confidence in regulation, cumulative link

ordinal_mod <- ordinal::clm(
  factor(election_reg, ordered = TRUE) ~ Training.condition,
  data = welch_df,
  link = "logit"
)

summary(ordinal_mod)

confint(ordinal_mod)

# odds ratio

OR <- exp(coef(ordinal_mod)["Training.condition1"])
CI <- exp(confint(ordinal_mod)["Training.condition1", ])

# assumption test

ordinal::nominal_test(ordinal_mod)

```
